Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2022-09-25 Documents/Bookdown/01-case-study.Rmd
update bookdown

Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version [ECR-RC, @Brenning2014ThePQ; marciBriefExperiencesClose2019] completed by the children. Four main attachment styles have been recognized in the literature according to thee levels of *anxiety* and *avoidance*:

@@

In Figure~\@ref(fig:plot-scores-mother), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to mother attachment styles. The frequencies of mother attachment styles according to gender are reported in Table~\ref{tab:table-cluster-mother}.

@@

In Figure~\@ref(fig:plot-scores-father), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to father attachment styles. The frequencies of father attachment styles according to gender are reported in Table~\ref{tab:table-cluster-father}.

@@

Overall, internalizing problems are low. Again, this is expected as the sample is not clinical. Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).

>>>>

Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version [ECR-RC, @Brenning2014ThePQ; @marciBriefExperiencesClose2019] completed by the children. Four main attachment styles have been recognized in the literature according to thee levels of *anxiety* and *avoidance*:

@@

In Figure~\@ref(fig:plot-scores-mother), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to mother attachment styles. The frequencies of mother attachment styles according to gender are reported in Table~\@ref(tab:table-cluster-mother).

@@

In Figure~\@ref(fig:plot-scores-father), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to father attachment styles. The frequencies of father attachment styles according to gender are reported in Table~\@ref(tab:table-cluster-father).

@@

Overall, internalizing problems are low. Again, this is expected as the sample is not clinical. Internalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-int).

### 2022-09-25 Documents/Bookdown/index.Rmd
update bookdown

--- 
title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Supplemental Material of the article “Evaluating informative hypotheses with equality and inequality constraint: A tutorial using the Bayes factor via the encompassing prior approach”"
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

@@

devtools::load_all("../../")
source("../Utils_report.R")

#----    load drake    ----

drake_load_bookdown()
```

>>>>

--- 
title: "Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Supplemental Material of the article “Evaluating informative hypotheses with equality and inequality constraint: A tutorial using the Bayes factor via the encompassing prior approach”"
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

@@

devtools::load_all("../../")

#----    load targets    ----

tar_load_bookdown(store = "../../Analysis/_targets/")
```
